---
title: "Invariância"
author: "Nayara"
date: "7/2/2020"
output: word_document
---

First of all, we need to understand the concept of the invariance of the AFC model. For this, I recommend reading this article, which is very didactic: https://www.scielo.br/pdf/pusf/v18n2/v18n2a05.pdf.
Got it done, good luck (lol). Just kidding, just follow the steps below.


##Puxando os pacotes
```{r}
library(lavaan)
library(devtools)
library(semTools)
library(mirt)
library(readxl)
library(mice)
library(merTools) #to calculate the ICC
library(jtools)   #to present the regression results in table (more organized) 
library(lmerTest)
library(reghelper) 
```


##Load data set and take the missings out
```{r set up data}
invarianciaCAAS <- read_excel("C:/Users/nayar/Dropbox/Doutorado/Projeto Doutorado/Projeto/Estudo 2 - Validação CAAS/Validação AFC/ImpCAAS_treinador_atletaTodos.xlsx") ##Load data set


colnames(invarianciaCAAS)
table(invarianciaCAAS$Sexo)
table(invarianciaCAAS$`T ou A`)
invarianciaTA = invarianciaCAAS[,c(11:30)] ##take just the interest variables
View(invarianciaTA)
#invarianciaCAAS <- invarianciaCAAS[,c(12:30)]
fcaas<-na.omit(invarianciaCAAS) ##Verify and take the missings out
fcaasTA<-na.omit(invarianciaTA) ##Verify and take the missings out
```



#Defining the model (factors and items) 
```{r}
caas.model<-'
Avoidant =~ AP01 + AP02 + AP03 + AP04 + AP05 + AP06 + AP07
			 Anxious =~ AP08 + AP09 + AP10 + AP11 + AP12 + AP13 + AP14
			 Secure =~ AP15 + AP16 + AP17 + AP18 + AP19
'


# estimating the fit of the model to the data
fcaas.fit<-cfa(caas.model, na.omit(invarianciaTA), estimator = "WLSMV", 
               ordered = colnames(invarianciaTA))
summary(fcaas.fit, fit.measures=T,standardized=TRUE)

# calculating the reliability of factors using McDonald's Omega
omega(fcaas.fit) 
```


##By group
```{r}
#by gender
fcaas.fitsexo<-cfa(caas.model,na.omit(invarianciaCAAS), estimator = "WLSMV",
                   ordered = colnames(invarianciaCAAS), group = "Sexo")
summary(fcaas.fitsexo,fit.measures=T,standardized=T)
#check the ladings differences


#by coach and athlete
invarianciaTA$TA <- invarianciaTA$`T ou A`

fcaas.fitTA<-cfa(caas.model,na.omit(invarianciaTA), estimator = "WLSMV",
                 ordered = colnames(invarianciaTA), group = "TA")
summary(fcaas.fitTA,fit.measures=T,standardized=T) #check the ladings differences
```



##Baseline invariance model
```{r by gender}
fcaasSEX.fit_inv <- measEq.syntax(configural.model = caas.model,
                                 data = invarianciaCAAS,
                                 ordered = colnames(invarianciaCAAS),
                                 parameterization = "delta",
                                 ID.fac = "std.lv",
                                 ID.cat = "Wu.Estabrook.2016",
                                 group = "Sexo",
                                 group.equal = c("configural","thresholds","loadings"))

model.inv <- as.character(fcaasSEX.fit_inv)

fcaasSEX.fit2 <- cfa(model.inv, data = invarianciaCAAS, group = "Sexo",
                    ordered =colnames(invarianciaCAAS))
summary(fcaasSEX.fit2,fit.measures=T,standardized=T)
```



```{r by coach and athlete}
fcaasTA.fit_inv <- measEq.syntax(configural.model = caas.model,
                                 data = invarianciaTA,
                                 ordered = colnames(invarianciaTA),
                                 parameterization = "delta",
                                 ID.fac = "std.lv",
                                 ID.cat = "Wu.Estabrook.2016",
                                 group = "TA",
                                 group.equal = c("configural","thresholds","loadings"))

model.inv <- as.character(fcaasTA.fit_inv)

fcaasTA.fit2 <- cfa(model.inv, data = invarianciaTA, group = "TA",
                    ordered =colnames(invarianciaTA))
summary(fcaasTA.fit2,fit.measures=T,standardized=T)
```


===============================
By invariances levels
===============================

##Configural
```{r by gender}
fcaasSEX.fit_conf <- measEq.syntax(configural.model = caas.model,
                                 data = invarianciaCAAS,
                                 ordered = colnames(invarianciaCAAS),
                                 parameterization = "delta",
                                 ID.fac = "std.lv",
                                 ID.cat = "Wu.Estabrook.2016",
                                 group = "Sexo",
                                 group.equal = "configural")

model.inv_conf <- as.character(fcaasSEX.fit_conf)

fcaasSEX.fit2_conf <- cfa(model.inv_conf, data = invarianciaCAAS, group = "Sexo",
                    ordered =colnames(invarianciaCAAS))
summary(fcaasSEX.fit2_conf,fit.measures=T,standardized=T)
```


```{r by coach and athlete}
fcaasTA.fit_conf <- measEq.syntax(configural.model = caas.model,
                                 data = invarianciaTA,
                                 ordered = colnames(invarianciaTA),
                                 parameterization = "delta",
                                 ID.fac = "std.lv",
                                 ID.cat = "Wu.Estabrook.2016",
                                 group = "TA",
                                 group.equal = "configural")

modelTA.inv_conf <- as.character(fcaasTA.fit_conf)

fcaasTA.fit2_conf <- cfa(modelTA.inv_conf, data = invarianciaTA, group = "TA",
                    ordered =colnames(invarianciaTA))
summary(fcaasTA.fit2_conf,fit.measures=T,standardized=T)
```




##Loadings
```{r by gender}
fcaasSEX.fit_load <- measEq.syntax(configural.model = caas.model,
                                  data = invarianciaCAAS,
                                  ordered = colnames(invarianciaCAAS),
                                  parameterization = "delta",
                                  ID.fac = "std.lv",
                                  ID.cat = "Wu.Estabrook.2016",
                                  group = "Sexo",
                                  group.equal =c("configural","loadings"))

model.inv_load <- as.character(fcaasSEX.fit_load)

fcaasSEX.fit2_load <- cfa(model.inv_load, data = invarianciaCAAS, group = "Sexo",
                         ordered =colnames(invarianciaCAAS))
summary(fcaasSEX.fit2_load,fit.measures=T,standardized=T)
```


```{r por coach and athlete}
fcaasTA.fit_load <- measEq.syntax(configural.model = caas.model,
                                  data = invarianciaTA,
                                  ordered = colnames(invarianciaTA),
                                  parameterization = "delta",
                                  ID.fac = "std.lv",
                                  ID.cat = "Wu.Estabrook.2016",
                                  group = "TA",
                                  group.equal =c("configural","loadings"))

modelTA.inv_load <- as.character(fcaasTA.fit_load)

fcaasTA.fit2_load <- cfa(modelTA.inv_load, data = invarianciaTA, group = "TA",
                         ordered =colnames(invarianciaTA))
summary(fcaasTA.fit2_load,fit.measures=T,standardized=T)
```


##Interceptos
```{r by gender}
fcaasSEX.fit_int <- measEq.syntax(configural.model = caas.model,
                                  data = invarianciaCAAS,
                                  ordered = colnames(invarianciaCAAS),
                                  parameterization = "delta",
                                  ID.fac = "std.lv",
                                  ID.cat = "Wu.Estabrook.2016",
                                  group = "Sexo",
                                  group.equal = c("configural","loadings","intercepts"))

model.inv_int <- as.character(fcaasSEX.fit_int)

fcaasSEX.fit2_int <- cfa(model.inv_int, data = invarianciaCAAS, group = "Sexo",
                         ordered =colnames(invarianciaCAAS))
summary(fcaasSEX.fit2_int,fit.measures=T,standardized=T)
```


```{r by coach and athlete}
fcaasTA.fit_int <- measEq.syntax(configural.model = caas.model,
                                  data = invarianciaTA,
                                  ordered = colnames(invarianciaTA),
                                  parameterization = "delta",
                                  ID.fac = "std.lv",
                                  ID.cat = "Wu.Estabrook.2016",
                                  group = "TA",
                                  group.equal = c("configural","loadings","intercepts"))

modelTA.inv_int <- as.character(fcaasTA.fit_int)

fcaasTA.fit2_int <- cfa(modelTA.inv_int, data = invarianciaTA, group = "TA",
                         ordered =colnames(invarianciaTA))
summary(fcaasTA.fit2_int,fit.measures=T,standardized=T)
```



##All the results summarized - how to report in the paper
```{r by gender}
all.results<-matrix(NA, nrow = 3, ncol = 6)
all.results[1,]<-round(data.matrix(fitmeasures
(fcaasSEX.fit2_conf, fit.measures = c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled"))), digits=3)
all.results[2,]<-round(data.matrix(fitmeasures
(fcaasSEX.fit2_load, fit.measures = c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled"))), digits=3)
all.results[3,]<-round(data.matrix(fitmeasures
(fcaasSEX.fit2_int, fit.measures = c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled"))), digits=3)
colnames(all.results)<-c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled")
all.results
#Para verificar qual parametro comparar para confirmar a invariancia do modelo, ver:
#https://www.tandfonline.com/doi/abs/10.1080/10705511.2019.1602776?journalCode=hsem20. Tem uma tabela otima, baseada em alguns criterios (numero de fatores, n dos grupos, etc.)
```



```{r by coach and athlete}
all.results<-matrix(NA, nrow = 3, ncol = 6)
all.results[1,]<-round(data.matrix(fitmeasures
(fcaasTA.fit2_conf, fit.measures = c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled"))), digits=3)
all.results[2,]<-round(data.matrix(fitmeasures
(fcaasTA.fit2_load, fit.measures = c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled"))), digits=3)
all.results[3,]<-round(data.matrix(fitmeasures
(fcaasTA.fit2_int, fit.measures = c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled"))), digits=3)
colnames(all.results)<-c("chisq.scaled","df.scaled","pvalue.scaled", "rmsea.scaled", "cfi.scaled", "tli.scaled")
all.results
```


#Delta (chisq - chisq)
```{r}
1056.488 - 1138.614 #chisq[1] - chisq[2]
1138.614 - 1131.666 #chisq[2] - chisq[3]

0.964 - 0.961 #tli[1] - tli[2]
0.961 - 0.961 #tli[2] - tli[3]
```




























