---
title: "cpg_arima"
author: "Cyrus Elahi"
date: "February 5, 2019"
output: html_document
---


```{r }
library(tidyverse)
library(ggplot2)
library(stringr)
library(forcats)
library(lubridate)
library(likert)
library(survival)
library(splines)
library(forecast)
#library(patchwork)
```


```{r}
#Doesnt have days til death
setwd("C:/Users/cyrus/OneDrive/Documents/R/input")
tbi <- read.csv("tz_TBIregistry_data.csv")
```

trying out a new dataset. I will not get rid of those with negative endpoints. 
so increased sample size
```{r}
#by gcs
tbi <- tbi %>%
  dplyr::select(study_id, 
                date_arrival, 
                time_arrival, 
                tbi_surgery, 
                ct_brain, death, 
                nurse_vs, 
                date_death, 
                cd_dispo, 
                time_death, 
                date_dc_home, 
                gcs_tot, 
                gos, 
                gose, 
                male, 
                moi, 
                alcohol, 
                surgtoicu, 
                age,
                fluids,
                sys_bp,
                dia_bp,
                oxygen,
                pulse_ox,
                heart_rate,
                resp_rate,
                cxr)

#there is no time home. So i will operate under the assumption that time home is always 23:59. This if arrival and d/c occur same day, I will not get a negative difference between the two
tbi$time_home <- "23:59"

#converting dates to numeric early
tbi$date_arrival2 <- (strptime  ( paste(tbi$date_arrival, tbi$time_arrival), "%m/%d/%Y %H:%M"))
tbi$date_death2   <- (strptime  ( paste(tbi$date_death, tbi$time_death), "%m/%d/%Y %H:%M") )
tbi$date_home2    <- (strptime  ( paste(tbi$date_dc_home, tbi$time_home), "%m/%d/%Y %H:%M"))

#when dates already numeric
tbi$arrival_death <- round(as.numeric( difftime(tbi$date_death2, tbi$date_arrival2, units = "days")), 2)
tbi$arrival_home  <- round(as.numeric( difftime(tbi$date_home2 , tbi$date_arrival2, units = "days")), 2)

#error message unless run this line to convert date to date format
tbi$date_arrival2 <- as.Date(tbi$date_arrival2)

#by gcs
tbi <- tbi %>%
    dplyr::select(study_id, 
                  date_arrival2,  
                  tbi_surgery, 
                  death, 
                  nurse_vs, 
                  ct_brain, 
                  cd_dispo, 
                  time_death, 
                  gcs_tot, 
                  gos, 
                  gose, 
                  arrival_home, 
                  arrival_death, 
                  male, 
                  moi, 
                  alcohol, 
                  surgtoicu, 
                  age,
                  fluids,
                  sys_bp,
                  dia_bp,
                  oxygen,
                  pulse_ox,
                  heart_rate,
                  resp_rate,
                  cxr) %>%
    mutate(endpt = if_else(is.na(tbi$arrival_death == TRUE), arrival_home, arrival_death)) 

#aggregate all outcomes associated to gos and gose variables trying to reduce missings                                   
tbi$gose_recoded<- car::recode(tbi$gose, "1=1;2=2;3:4=3;5:6=4;7:8=5;else=NA")
tbi$gos_complete <- ifelse(is.na(tbi$gose_recoded) & is.na(tbi$gos),NA,
                                   ifelse(is.na(tbi$gose_recoded),tbi$gos,
                                          ifelse(is.na(tbi$gos),tbi$gose_recoded,tbi$gos)))
#Change the type of variables accordingly to the codebook.
tbi$gos_complete <- factor(tbi$gos_complete, 
                           labels = c("Death", "Persistent Vegetative", "Severe Disability", "Moderate Disability", "Good recovery"))

#we need to decide what consitutes good vs poor recovery. is moderate disability considered a win??
tbi$gos_outcome <- car::recode(tbi$gos_complete, "'Death' = 'Bad Recovery';
                                   'Persistent Vegetative' = 'Bad Recovery';
                                   'Severe Disability' = 'Bad Recovery';
                                   'Moderate Disability' = 'Bad Recovery'") 
tbi$moi <- car::recode(tbi$moi, "'3' = '2';
                       '4' = '2'")

#####REGULAR alternative
test <- tbi %>%
  mutate(gcs_facet = case_when(gcs_tot <=8 ~ "severe",
                               gcs_tot >= 9 & gcs_tot <= 12 ~ "mod",
                               gcs_tot >= 13 ~ "mild")) %>%
  mutate(gos_outcome_num = case_when(gos_outcome == "Good recovery" ~ 0,
                                     gos_outcome == "Bad Recovery" ~ 1))


#removing Nas from the whole dataset
test6 <- test[!is.na(test$gos_outcome_num),]

#getting rid of rouge 2 on tbi surgery
#test6 <- subset(test2, test3$tbi_surgery < 2)

#making a column of 1s to later count for total of surgery
test6$volume <- test6$gos_outcome_num
test6$volume <- car::recode(test6$volume, "'0' = '1';
                                   '1' = '1'")

test6$nurse_vs <- as.numeric(car::recode(test6$nurse_vs, "2 = NA"))

#creating clinical need variables to measure medical team performance
test6 <- test6 %>% mutate(ct_need = case_when(gcs_tot < 13 ~ 1,
                                     TRUE ~ 0)) %>%
                   mutate(ct_noneed = case_when(gcs_tot >= 13 ~ 1,
                                     TRUE ~ 0)) %>%
                   mutate(ct_received = case_when(ct_brain == "1" & gcs_tot < 13 ~ 1,
                                                  TRUE ~ 0)) %>%
                   mutate(ct_received_noneed = case_when(ct_brain == "1" & gcs_tot >= 13 ~ 1,
                                                  TRUE ~ 0)) %>%
                   mutate(hypoten = case_when(sys_bp < 90 | dia_bp < 60 ~1,
                                              TRUE ~ 0)) %>%
                   mutate(hypoten_noneed = case_when(sys_bp >= 90 & dia_bp >= 60 ~1,
                                              TRUE ~ 0)) %>%
                   mutate(fluids_received = case_when(hypoten =="1" & fluids == "1" ~ 1,
                                                      TRUE ~ 0)) %>%
                   mutate(fluids_received_noneed = case_when(hypoten =="0" & fluids == "1" ~ 1,
                                                      TRUE ~ 0)) %>%                   
                   mutate(hypoxic = case_when(pulse_ox < 92 | gcs_tot < 8 ~ 1,
                                              TRUE ~ 0)) %>%
                   mutate(hypoxic_noneed = case_when(pulse_ox >= 90 & gcs_tot >= 8 ~ 1,
                                              TRUE ~ 0)) %>%
                   mutate(oxy_received = case_when(hypoxic == "1" & oxygen == 1 ~ 1,
                                                   TRUE ~ 0)) %>%
                   mutate(oxy_received_noneed = case_when(hypoxic == "0" & oxygen == 1 ~ 1,
                                                   TRUE ~ 0)) %>%
                   mutate(need_cxr = case_when(hypoxic == "1" | heart_rate > 100 | resp_rate > 20 | gcs_tot < 14 ~ 1,
                                               TRUE ~ 0)) %>%
                   mutate(noneed_cxr = case_when(hypoxic == "0" & heart_rate <= 100 & resp_rate <= 20 & gcs_tot >= 14 ~ 1,
                                               TRUE ~ 0)) %>%
                   mutate(cxr_received = case_when(need_cxr == "1" & cxr == 1 ~ 1,
                                                   TRUE ~ 0)) %>%
                   mutate(cxr_received_noneed = case_when(need_cxr == "0" & cxr == 1 ~ 1,
                                                   TRUE ~ 0))

```

test6 is a dataset that is now ready to prep for a timeseries analysis. 
##for full dataset
```{r}
# #summing by month
# 
# data1 <- test6 %>%
#   group_by(month=floor_date(date_arrival2, "month")) %>%
#   summarise(badrecov_sum = sum(gos_outcome_num),
#             death_sum = sum(death),
#             volume_month = sum(volume),
#             br_prop = sum(gos_outcome_num) / sum(volume),
#             death_prop = sum(death) / sum(volume)
#             )
# data2 <- data1[6:49,]
# #data2 <- data1[35:46, ]

```

test6 is a dataset that is now ready to prep for a timeseries analysis. 
##for dataset after the missing month due to IRB renewal <- this is the one we are using.
```{r}
#summing by month
##Data one and two are for time trend type of data
data1 <- test6 %>%
  group_by(month=floor_date(date_arrival2, "month")) %>%
  summarise(badrecov_sum = sum(gos_outcome_num, na.rm = TRUE),
          #  br_sum_severe = sum(gos_outcome_num[gcs_facet == "severe"]),
          #  br_sum_mod = sum(gos_outcome_num[gcs_facet == "mod"]),
          #  br_sum_mild = sum(gos_outcome_num[gcs_facet == "mild"]),
          vitals = sum(nurse_vs, na.rm = TRUE),
            death_sum = sum(death, na.rm = TRUE),
            volume_month = sum(volume),
            cxr_prop = sum(cxr_received, na.rm = TRUE) / sum(need_cxr, na.rm = TRUE),
            noneed_cxr_prop = sum(cxr_received_noneed, na.rm = TRUE) / sum(noneed_cxr, na.rm = TRUE),
            oxy_prop = sum(oxy_received, na.rm = TRUE) / sum(hypoxic, na.rm = TRUE),
            noneed_oxy_prop = sum(oxy_received_noneed, na.rm = TRUE) / sum(hypoxic_noneed, na.rm = TRUE),
            fluids_prop = sum(fluids_received, na.rm = TRUE) / sum(hypoten, na.rm = TRUE),
            noneed_fluids_prop = sum(fluids_received_noneed, na.rm = TRUE) / sum(hypoten_noneed, na.rm = TRUE),
            ct_prop = sum(ct_received, na.rm = TRUE) / sum(ct_need, na.rm = TRUE),
            noneed_ct_prop = sum(ct_received_noneed, na.rm = TRUE) / sum(ct_noneed, na.rm = TRUE),
            vitals_prop = sum(nurse_vs, na.rm = TRUE) / sum(volume, na.rm = TRUE),
            br_prop = sum(gos_outcome_num, na.rm = TRUE) / sum(volume),
            death_prop = sum(death, na.rm = TRUE) / sum(volume, na.rm = TRUE)
            ) %>%
  mutate(vitals_prop = rollmean(vitals_prop, 3, fill = NA)) %>%
  mutate(cxr_prop = rollmean(cxr_prop, 3, fill = NA)) %>%
  mutate(oxy_prop = rollmean(oxy_prop, 3, fill = NA)) %>%
  mutate(fluids_prop = rollmean(fluids_prop, 3, fill = NA)) %>%
  mutate(ct_prop = rollmean(ct_prop, 3, fill = NA)) 

data2 <- data1[17:49,]

```


ARIMA
```{r}
timeseries_data_all <- ts(data2$br_prop, #data$distracteddriving , 
                          start=c(2014,7), end = c(2017,3),frequency=12)
#find out # of differences
#pvalue > .05
timeseries_data_all %>% adf.test()

#pvalue < .05
####This tells me one diff is needed to reach significance
diff(timeseries_data_all) %>%
   #diff() %>%
  #diff() %>%
  adf.test() 

###One difference is also needed for the deseasonal data. Not surprising. =
#deseasonal %>% adf.test #pvalue > .05
#diff(deseasonal) %>%
  # diff() %>%
  #diff() %>%
#  adf.test() 


#diff_data <- diff(deseasonal)# %>% adf.test #pvalue < .05

Acf(timeseries_data_all)
Pacf(timeseries_data_all)

Acf(new)
Pacf(new)


Acf(deseasonal)
Pacf(deseasonal)


intervention <- c(rep(0,24), 1:9)

fit <- Arima(timeseries_data_all, c(1, 1, 1), seasonal = c(1,1,1), xreg = intervention)
fit
#may need to run this first
dev.off()
tsdisplay(residuals(fit), lag.max=33, main='(1,2,1) Model Residuals')

#extract coeff of the model (do i exponentiate like an odds ratio?) need to figure out what to export
output <- as.data.frame(cbind(coef = fit$coef, fit$aic))


acf(fit$residuals)
pacf(fit$residuals)

```